%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\usepackage[bitstream-charter]{mathdesign}
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\openSourceSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
     \vspace{4pt} \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}\vspace{-6pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\textbf{\href{https://www.linkedin.com/in/zsshen/}{\Large Zong-Xian (Andy) Shen}} & Email : \href{mailto:andy.zsshen@gmail.com}{andy.zsshen@gmail.com}\\
	\href{https://www.linkedin.com/in/zsshen/}{https://www.linkedin.com/in/zsshen/} & Mobile : +1-650-770-5999 \\
\end{tabular*}

%-----------SUMMARY-----------------
\section{Summary}
\small Software engineer with 5 years of experience in \textbf{e-Commerce backend} and cloud computing seeking fulltime SDE/infrastructure roles. Expertise in \textbf{scalable data pipelines} and \textbf{large-scale cloud orchestration}, evidenced by building an \textbf{Ads infra} serving 1M+ QPS. Open-source developer contributing to various projects, including \textbf{Mozilla’s JavaScript Just-in-Time compiler}.

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Carnegie Mellon University}{Mountain View, CA}
{M.S. in Software Engineering;  GPA: 3.74/4}{Aug. 2019 -- Dec. 2020}
\resumeSubheading
{National Chiao Tung University}{Hsinchu, Taiwan}
{M.S./B.S. in Computer Science; GPA: 4/4 (M.S.), 3.14/4 (B.S.)}{Sep. 2007 -- July. 2013}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Amazon}{Seattle, WA}
{Security Engineer Intern, Vulnerability Research Program}{May. 2020 -- Aug. 2020}

\resumeItemListStart
\vspace{3pt}
\item{Enhanced the \textbf{cyberthreat analytics} platform by building a new service with \textbf{Java Spring} running on \textbf{ECS}, a new data pipeline with \textbf{CloudWatch}, \textbf{Lambda}, and \textbf{DynamoDB}, and a new metrics dashboard with \textbf{QuickSight} and \textbf{Redshift}}

\item{Researched threat incident reports regarding \textbf{XSS} and \textbf{CSRF} attacks against amazon.com and the subsidiaries}

\resumeItemListEnd

\resumeSubheading
{Appier Inc.}{Taipei, Taiwan}
{Software Engineer, Realtime Bidding \& Ads Infrastructure}{Nov. 2016 -- Jun. 2019}

\vspace{3pt} \small {Worked as a Scrumban team of 9 to build scalable realtime bidding system with \textbf{1K+} servers to serve \textbf{1M+} QPS}
\resumeItemListStart
\item{Boosted the QPS by \textbf{20X} and doubled the business revenue by constructing a new bidding system on \textbf{AWS} and \textbf{GCP}  with C++ 14/17 Ads funnel backend running on \textbf{Nginx} and a new data pipeline built by \textbf{PostgreSQL} and \textbf{Prometheus}}

\item{Reduced orchestration and alert response time of the bidding system by \textbf{30X} through constructing a money flow
      tracking and server performance monitoring system with \textbf{Ansible}, \textbf{Kafka}, \textbf{Cassandra}, and \textbf{Grafana}}

\resumeItemListEnd

\resumeSubheading
{Trend Micro Inc.}{Taipei, Taiwan}
{Software Engineer, Core Malware Detection Engine}{Sep. 2013 -- Nov. 2016}

\vspace{3pt} \small{Worked in a global engineering group to develop scan engine and detection signatures to protect \textbf{250M+} endpoints}
\resumeItemListStart
\item{Boosted the throughput of engine and signature verification platform by \textbf{24X} using \textbf{Docker} and
      \textbf{Kubernetes} to simplify and balance the workload of test units running on \textbf{VMWare's vSphere}}

\item{Create an ML-powered malware classifier using \textbf{XGBoost} and bytecode n-gram for .NET malware detection, yielding \textbf{98\%} detection rate for \textbf{5M+} banked malware samples and \textbf{0.1\%} false alarm rate for \textbf{5M+} normal files}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Open Source Contribution}

\resumeSubHeadingListStart
\openSourceSubheading
{Mozilla, {\normalfont Compiler Developer} | {\normalfont Contribution Profile: https://mzl.la/2fO3bJQ}}{}
{}{}

\small Optimized the \textbf{Just-in-Time compiler} of \textbf{SpiderMonkey JavaScript engine} via control and data flow analysis to eliminate redundant bytecode and expressions, contributing to features deployed in Firefox 35 to boost web browsing experience

\openSourceSubheading
{GitHub, {\normalfont Open Source Contributor} | {\normalfont \textbf{2K+} Stars, All Projects Combined: https://github.com/ZSShen} }{}
{}{}

\small Created various programming utilities and profiling tools including a dynamic instrumentation kit to analyze Android malware, a \textbf{malware classifier} for signature generation, and a \textbf{cross-platform C data structure library} with \textbf{93\% unit test coverage}


\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Selected Academic Projects}

\resumeSubHeadingListStart

\resumeSubheading
{Code Snippet Recommendation Service}{Distributed System, CMU}
{High Performance Full-text Search Engine on \textbf{GCP} }{Spring 2020}

\vspace{3pt} \small {Led a team of 3 to build the engine supporting exact and fuzzy code snippet search with 500GB raw data set, achieving \textbf{13K+} QPS with \textbf{ElasticSearch} and \textbf{Memcached} hybrid backend running on 5 E2-standard-2 (2 CPU/8G RAM) nodes}

\resumeSubheading
{Emergency Social Network}{Foundations of Software Engineering, CMU}
{Chat Room-based Web Application}{Fall 2019}

\vspace{3pt}\small{Work as a team of 4 to build the social network app with 88\% test coverage using \textbf{Bootstrap}, \textbf{Express.js}, \textbf{MongoDB}, and \textbf{Axios}}


\resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
\resumeSubHeadingListStart
\item{
      Language/Development: \textbf{C++}, \textbf{C}, \textbf{Python}, \textbf{Java}, \textbf{JavaScript} / \textbf{CMake}, \textbf{GDB}, \textbf{Docker}
}
\vspace{-3pt}
\item{
      Frameworks/Operation/Stroage: \textbf{Java Spring}, \textbf{AWS}, \textbf{Node.js}, \textbf{Kafka}, / \textbf{Ansible}, \textbf{Jenkins} / \textbf{MySQL}, \textbf{Cassandra}, \textbf{Prometheus}
}
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}